\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}

\begin{document}

\title{Monday Reading Assessment: Unit 2, Two-dimensional kinematics}
\author{Prof. Jordan C. Hanson}

\maketitle

\section{Memory Bank}

\begin{itemize}
\item $\vec{x} = a \hat{i} + b\hat{j}$ ... Component form of a two-dimensional vector.
\item $|\vec{x}| = \sqrt{a^2+b^2}$ ... Pythagorean theorem for obtaining vector magnitude.
\item $\theta = \tan^{-1}(b/a)$ ... Obtaining the angle between vector and x-axis.
\item $a = |\vec{x}|\cos(\theta)$ ... Obtaining the x-component with trigonometry.
\item $b = |\vec{x}|\sin(\theta)$ ... Obtaining the y-component with trigonometry.
\item $\Delta x = \vec{x}_f - \vec{x}_i$ ... Definition of displacement.
\end{itemize}

\section{Chapter 3 - Two-Dimensional Kinematics}

\begin{enumerate}
\item Suppose Los Angeles is located at the origin of a 2D coordinate system with North in the positive y-direction and East in the positive x-direction.  A certain ship needs to sail from Los Angeles, California to Honolulu, Hawaii.  The ship heads almost directly West, but about 10 degrees South of West.  \textit{Draw a two-dimensional coordinate system below, indicating Los Angeles at the origin and Honolulu in the correct quadrant of the graph.} \\ \vspace{3cm}
\item (a) The distance between Los Angeles and Honolulu is 4100 kilometers.  Write the displacement the ship makes from Los Angeles to Honolulu in $\hat{i}$ $\hat{j}$ notation.  This will give the amount of distance \textit{West} (x-direction) and the amount of distance \textit{South} (y-direction) the ship must sail.  What should the \textit{sign} of each number be?  (b) Suppose the trip takes 5 days.  Divide the displacement by this time to obtain the velocity vector.  \\ \vspace{3cm}
\item Imagine that the ship secretly has a launcher capable of launching a capsule into space for a short time.  The ship is traveling with the velocity vector derived in the prior exercise, and shoots a space capsule straight up with no wind resistance.  Will the capsule land back on the ship if the ship keeps moving?  Why or why not?
\end{enumerate}

\end{document}
