\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}

\begin{document}

\title{Warm-Up 0: units, vectors, and introductory calculus}
\author{Prof. Jordan C. Hanson}

\maketitle

\section{Chapter 1 - Units and Measurement}

\begin{enumerate}
\item In your own words, what is a physics theory, and what determines the validity of a theory? \\ \vspace{0.5cm}
\item Which of the following is not correct?
\begin{itemize}
\item A: The quantity meters per second$^2$ is a unit of acceleration.
\item B: A kilometer is a unit of speed.
\item C: A kilometer per hour is a unit of speed.
\item D: The quantity kg per meter$^3$ is a unit of density.
\end{itemize}
\end{enumerate}

\section{Chapter 2 - Vectors}

\begin{enumerate}
\item Which of the following is should be considered a vector quantity (i.e. having a magnitude and direction)?
\begin{itemize}
\item A: wind velocity
\item B: air temperature
\item C: the mass of an object
\item D: the brightness of a light source
\end{itemize}
\item Explain in your own words (or draw a diagram): why can't a vector have a component greater than its own magnitude? \\ \vspace{1cm}
\end{enumerate}

\section{Mathematics Topic - The Slope of a Function, with Units}

\begin{enumerate}
\item The \textit{slope}, $m$, of a function $f(t)$ between times $t_i$ and $t_f$ is defined as 
\begin{equation}
m = \frac{f(t_f) - f(t_i)}{t_f - t_i}
\end{equation}
\item Find the slope of the following function: $f(t) = 4t - 2$ meters, with $t_f = 4$ seconds and $t_i = 2$ seconds. \vspace{1cm}
\item Find the slope of the following function: $f(t) = 2t^2 - 1$ meters, with $t_f = 3$ seconds and $t_i = 2$ seconds. \vspace{1cm}
\end{enumerate}

\end{document}
