\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}

\begin{document}

\title{Wednesday Reading Assessment: Unit 2, Two-dimensional kinematics}
\author{Prof. Jordan C. Hanson}

\maketitle

\section{Memory Bank}

\begin{itemize}
\item $|\vec{x}| = \sqrt{a^2+b^2}$ ... Pythagorean theorem for obtaining vector magnitude.
\item $\theta = \tan^{-1}(b/a)$ ... Obtaining the angle between vector and x-axis.
\item $a = |\vec{x}|\cos(\theta)$ ... Obtaining the x-component with trigonometry.
\item $b = |\vec{x}|\sin(\theta)$ ... Obtaining the y-component with trigonometry.
\end{itemize}

\section{Chapter 3 - Two-Dimensional Kinematics}

\begin{enumerate}
\item Suppose an object is launched straight upwards.  Which of the following is true?
\begin{itemize}
\item A: The acceleration is negative the whole time.
\item B: The acceleration is negative, then zero, then positive.
\item C: The acceleration is negative, then zero, then negative.
\item D: The acceleration is positive the whole time.
\end{itemize}
\item An object is moving at 10 m/s, and in 5 seconds, it comes to a stop.  What is the acceleration?
\begin{itemize}
\item A: 2 m/s$^2$
\item B: -2 m/s
\item C: -1 m/s$^2$
\item D: -2 m/s$^2$
\end{itemize}
\item Suppose an object is launched at a 30 degree angle with respect to the horizontal direction.  Which of the following is true?
\begin{itemize}
\item A: The horizontal acceleration is negative the whole time.
\item B: The vertical acceleration is negative, then zero, then positive.
\item C: The horizontal acceleration is negative, then zero, then negative.
\item D: The horizontal acceleration is zero the whole time.
\end{itemize}
\item An initial velocity vector is $\vec{v}_i = (3\hat{i}+6\hat{j})$ m/s.  What is the angle it makes with the x-axis?  \textit{Hint: draw it to be sure}. \\ \vspace{2cm}
\item An initial velocity vector is $\vec{v}_i = (-2\hat{i}-4\hat{j})$ m/s.  What is the angle it makes with the x-axis?  \textit{Hint: draw it to be sure}. \\ \vspace{2cm}
\end{enumerate}
\end{document}
