\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{csquotes}

\begin{document}

\title{Physics Department Self-Study: Laboratory Activities}
\author{Prof. Jordan C. Hanson}

\maketitle

\section{Instructions}

The purpose of this survey is to understand how the laboratory activities in PHYS135A function in the course.  The American Association of Physics Teachers (AAPT) recommends several categories of laboratory experiments, including Peer Instruction (the clickers).  and We do our best at Whittier College to touch upon all of the categories, but inevitably there are time constraints.  Please circle a choice below according to the following scale: (1) Disagree (2) Moderately disagree (3) Neutral (4) Moderately agree (5) Agree.

\section{Student Responses}

\begin{enumerate}
\item The laboratory activities in this course have helped me practice testing a scientific model or hypothesis. \\ ... (1) (2) (3) (4) (5)
\item The laboratory activities in this course have helped me to practice troubleshooting an experiment. \\ ... (1) (2) (3) (4) (5)
\item The laboratory activities in this course have helped me to practice analyzing data. \\ ... (1) (2) (3) (4) (5)
\item The laboratory activities in this course have helped me practice designing my own experiment to test a hypothesis. \\ ... (1) (2) (3) (4) (5)
\item The peer-instruction (clicker) activities in this course have helped me to understand physics concepts. \\ ... (1) (2) (3) (4) (5)
\item The peer-instruction (clicker) activities in this course have helped me to practice communicating physics ideas to my peers. \\ ... (1) (2) (3) (4) (5)
\item The self-designed final project in this course have helped me practice designing my own experiment to test a hypothesis. \\ ... (1) (2) (3) (4) (5)
\item The self-designed final project in this course have helped me to practice communicating physics ideas to my peers. \\ ... (1) (2) (3) (4) (5)
\end{enumerate}

\end{document}
