\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}

\begin{document}

\title{Monday Reading Assessment: Unit 2, Kinematics}
\author{Prof. Jordan C. Hanson}

\maketitle

\section{Memory Bank}

\begin{enumerate}
\item Assume that acceleration is constant: $a = 3.0$ (m/s$^2$), and that $\Delta x = x_f - x_i$
\item $v_f(t) = at + v_{i}$ (m/s)
\item $x(t) = \frac{1}{2}at^2 + v_{i} t + x_{i}$ (m)
\item $v_f^2 = v_i^2 + 2a\Delta x$ (m/s)$^2$.
\end{enumerate}

\section{Chapter 3 - Vectors (and review of units)}

\begin{enumerate}
\item Suppose Captain Jack Sparrow is marooned on a small island in the Caribbean sea.  The wind is blowing due West at 10 km/hr.  He creates a raft and sets sail, moving West at 10 km/hr.  After 2 hours, the wind shifts to the North East, and has a speed of 10 km/hr.  One hour later, the wind shifts West again, at 10 km/hr.  What is Jack's final location, relative to the island? (\textit{Hint: draw a picture}). \\ \vspace{3cm}
\item Let $\vec{v} = v_x \hat{i} + v_y \hat{j}$, and $\vec{u} = u_x \hat{i} + u_y \hat{j}$.  Compute the following:
\begin{itemize}
\item $\vec{v} + \vec{u}$, if $v_x = 4$ m/s, $v_y = -2$ m/s, $u_x = 0$ m/s, and $u_y = 2$ m/s.
\item $\vec{v} \cdot \vec{u}$, if $v_x = 4$ m/s, $v_y = -2$ m/s, $u_x = 0$ m/s, and $u_y = 2$ m/s.
\end{itemize}
\end{enumerate}

\section{Chapter 3 - Addition of Velocities}

\begin{enumerate}
\item Imagine you are playing rugby, carrying the ball and running down the field.  A teammate runs beside you, and you pass them the ball.  Answer yes or no: can they catch the ball if:
\begin{itemize}
\item A: They are running much faster than you
\item B: They are running much slower than you
\item C: They are running at the same speed as you.
\end{itemize}
\item Imagine the same scenario, except your teammate is running behind you.  If you are running at 6 m/s, and they are also running at 6 m/s, and you pass the ball \textit{backwards} at -3 m/s, what is the speed of the ball relative to the ground?
\end{enumerate}

\end{document}
