\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}

\begin{document}

\title{Wednesday Reading Assessment: Unit 1, Acceleration and Kinematics}
\author{Prof. Jordan C. Hanson}

\maketitle

\section{Chapter 2 - Kinematics}

\begin{enumerate}
\item Plus and minus signs are used in one-dimensional motion to indicate direction. What is the sign of an acceleration that
reduces the magnitude of a negative velocity? Of a positive velocity? \\ \vspace{3cm}
\item What is the acceleration of a rock thrown straight upward on the way up? At the top of its flight? On the way down? \\ \vspace{3cm}
\item Which of the following is true of a rock thrown straight upwards that is being accelerated downwards by gravity?
\begin{itemize}
\item A: The vertical displacement versus time is a quadratic curve with a peak at the maximum height.
\item B: The vertical displacement versus time is a linear line.
\item C: The vertical displacement versus time is a flat line.
\item D: The vertical displacement versus time is a quadratic curve with a valley at the minimum height.
\end{itemize}
\item Which of the following is true of a car that is decelerating because the driver is pressing the brake pedal?
\begin{itemize}
\item A: The horizontal velocity versus time is a quadratic curve with a peak at the maximum height.
\item B: The horizontal velocity versus time is a linear line with negative slope.
\item C: The horizontal velocity versus time is a linear line with positive slope.
\item D: The horizontal velocity versus time is a quadratic curve with a valley at the minimum height.
\end{itemize}
\end{enumerate}

\end{document}
