\title{Study Guide for Midterm 1 for Algebra-Based Physics-2: Electricity, Magnetism, and Modern Physics (PHYS135B-01)}
\author{Dr. Jordan Hanson - Whittier College Dept. of Physics and Astronomy}
\date{\today}
\documentclass[10pt]{article}
\usepackage[a4paper, total={18cm, 27cm}]{geometry}
\usepackage{outlines}
\usepackage[sfdefault]{FiraSans}
\usepackage{hyperref}
\begin{document}
\maketitle

\begin{enumerate}
\item \textbf{Working with orders magnitude, and approximation.} Use the following information: there are 107 grams per mole of silver, $\approx 6 \times 10^{23}$ atoms per mole, and one conducting electron per silver atom. 
\begin{enumerate}
\item Estimate the number of free electrons in 1 gram of silver. \\ \\ $5.6 \times 10^{21}$ \\
\item If $10^{10}$ conducting electrons are removed every $10^{-10}$ seconds, how long would it take to remove them all? (Think of this as a current). \\ \\ 56 seconds \\
\end{enumerate}
\item \textbf{The Coulomb force, and static charge.} The Coulomb force between two charges $q_1$ and $q_2$ separated by a distance $r$ is 
\begin{equation}
 	\vec{F}_C = k\frac{q_1 q_1}{r^2}\hat{r}
\end{equation}
The vector $\hat{r}$ is a unit vector pointing from one charge toward the other, and $k = 9\times 10^9$ N C$^{-2}$m$^{2}$.  Suppose $q_1 = 4.0 \mu$C, and $q_2 = 4.0 \mu$C, and $r=4.0 \mu$m. \\
\begin{enumerate}
\item What is the magnitude of the force between the charges, and in which direction does the force point? \\ \\ $9 \times 10^9$ N \\
\end{enumerate}
\item \textbf{Drawing electric field lines, 1.} Recall our experience with the PHeT simulation of charges and fields.  (a) Create a charge distribution of two opposite charges $\pm q$. (b) Illustrate the correct electric field between the charge distributions by drawing electric field lines. \\ \\ Remember: test charges are positive.  Electric field lines originate in positive charges and terminate on negative charges.  This means that the Coulomb force $F = qE$ on a test charge $q$ will push the positive test charge away from positive charges and pull them towards negative charges. \\
\item \textbf{Electric potential and electric field.} Recall that the relationship between a uniform electric field $E$ and the associated change in voltage $V$ is $V = Ed$, where $d$ is a distance.  Two uniformly charged plates with charges $+Q$ and $-Q$ create a uniform electric field $E$ between them.  Let the voltage at the negatively charged plate be 0 V.
\begin{enumerate}
\item 	If the distance between the plates is 80 mm, and the electric field has a value of 0.8 V/mm, what is the voltage at the positive plate? \\ \\ 64 V \\
\end{enumerate}
\item \textbf{Capacitors, and capacitance.} Recall that the charge $Q$ stored on a capacitor is $CV$ for a given potential $V$, and that the unit of capacitance is the \textit{Farad}, F.
\begin{enumerate}
\item How much charge is stored on a capacitor with $C = 0.1\mu$F, if the voltage is $V = 12$ V? \\ \\ $1.2 \mu C$ \\
\end{enumerate}
\item \textbf{Definition of current, resistance, and Ohm's Law} Recall that \textit{current} is the change in charge per unit time, $I = \Delta Q/\Delta t$, and that the unit of current is the \textit{amp}, A, which is 1 C/s.  Also recall that Ohm's Law is $V=IR$, where $V$ is the voltage, $I$ is the current, and $R$ is the total effective resistance.
\begin{enumerate}
\item How much current flows through a circuit that lights a lightbulb, if the voltage is 24 V, and the lightbulb has a resistance of $100$ Ohms? \\ \\ 240 mA \\
\item Recall that the relationship between the power $P$ consumed by a resistor drawing a current $I$ while being given a voltage $V$ is $P=IV$.  How many watts does the light bulb consume? \\ \\ 5.76 W \\
\item Draw a graph of voltage versus current for the lightbulb in part (a), assuming the voltage can vary.\\ \\ Should be a linear plot, since resistance is constant.  Resistance is the slope, if the plot is voltage versus current.  If the plot is current versus voltage, then the slope is 1/R. \\
\item Suppose the second light bulb is instead connected \textit{in parallel} with the first light bulb.  What is the new current? \\ \\ The resistance is cut in half so the current must double, according to Ohm's law.  Thus, the current is $2*240$ mA = 480 mA.
\end{enumerate}
\item \textbf{Nerve signals.} Please review the section of Chapter 20 on nerve signal conduction.  Pay special attention to the \textit{action impulse}, which is a voltage versus time. \\ \\ (See reading) \\
\end{enumerate}
\end{document}