\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}
\usepackage{url}
\begin{document}

\title{Asynchronous Activity: Potential of a Line of Charges}
\author{Prof. Jordan C. Hanson}

\maketitle

\section{How to Submit this Worksheet}

\begin{enumerate}
\item Scan your responses into a PDF using a Smartphone app, or simply a photo.  One example app is SimpleScanner.  Websites also exist to convert jpg to PDF format (e.g. \url{https://smallpdf.com/jpg-to-pdf}).
\item Upload your worksheet PDF to Moodle via the submission link.
\end{enumerate}

\section{The Procedure}

\begin{itemize}
\item Use the PhET Charges and Fields tool to create a line of positive charges parallel to a line of negative charges, as shown in class.
\item Using the blue voltage measurement tool, and the yellow distance measuring tool, record the voltage as a function of distance between the parallel lines of positive and negative charge.
\item Take 10-15 measurements at regular intervals.
\item Graph the data, and label the axes with the right units.
\item Use the trend line feature of the plotted data set to add a \textit{linear} fit.
\item Include your graph below (you can hand draw it or copy it from the spreadsheet).
\item Answer the questions below.
\end{itemize}

\section{Questions}

\begin{enumerate}
\item If $E = - \Delta V / \Delta x$, explain why the $\Delta V$ as a function of $x$ in this system is linear.
\item Use the linear trendline to predict a voltage at a location where you did not collect a data point (\textit{interpolation}).
\end{enumerate}

\vspace{10cm}

\end{document}
